### 2024-02-19 revision/reply_to_reviewer1.tex

	One takeaway message from Figure 7 is that the impact of negative numbers depends strongly on the spatial configuration of these negative numbers---in the first example (columns 1 and 2 in Figure 7), the negative numbers have minimal impact on the ellipsoid impulse response support estimates, whereas in the second example (columns 3 and 4), even a small amount of negative numbers causes the impulse response support estimate to be poor. The configuration of negative numbers for the integral kernel in wave inverse problem Hessians (including Gauss-Newton Hessians) is similar to that of the second example, and therefore our method is unlikely to be effective for wave Hessians.

	Although the component of the wave inverse problem Hessian corresponding to reflected waves is local, the component corresponding to transmission waves is non-local, which also poses challenges for our method (as discussed in the revised version of Section 3.2). If one applied a high-pass filter to remove the transmission component, in principle the impulse responses could be localized. However, the non-negativity would still need to be addressed.

	In Figure \ref{fig:marmousi_impulse} here (but not in the paper due to page limitations), we show an impulse response for the Gauss-Newton Hessian for the Marmousi wave inverse problem. Note that the non-local component of the impulse response shifts the mean far away from the visual ``center'' of the impulse response, and causes the ellipsoid impulse response support estimate to be effectively the entire domain.

	We also added more references and discussion regarding the wave inverse problem Hessian at the end of Section 2 in the revised manuscript.

@@

  	Frog example with a=1. Error vs \#batches, for different tau. Also do a plot with \#impulses on the x-axis.

  	Nick will try to create a plot that shows some error
    (e.g. Frob norm, cond number) as a function of number of impulse
    responses.}

 \item \referee{The paper presented a nice complexity analysis of the
   steps in constructing the approximate Hessian, with the dominating
   cost arising from the Hessian matrix-vector product. It would be
   interesting to see the computational time of each step for the
   numerical examples to provide a good sense of the complexity and to
   support the 5-10X computational reduction by accounting also the
   overhead beyond the PDE solves.}

   \noindent{We agree with the reviewer that there is an ``overhead''
     beyond the PDE applies. However, for all numerical tests we
     present in this paper, this cost was small compared to
     PDE-applies. This is due to the need for a relatively small
     number of sample points ($m$) in all batches. Since we have not
     invested time to optimize our codes for performance, it would be
     perhaps misleading to report profilingtiming information. When
     $m$ is very large, one can reduce this cost with more involved
     computational geometry methods. This was beyond the scope of our
     work.

     In the revised manuscript, following the other reviewer's
     suggestion, we added a comparison of the computational cost
     (measured in operator applies) to approximate the spacially
     varying blurring kernel example using the proposed PSF method,
     the randomized HODLR (hierarchical off diagonal low rank) method,
     and GLR (global low rank) approximation using randomized SVD. The
     results show an overwhelming computational gain for this
     particular example.}

### 2024-02-19 revision/letter_revision.tex
added draft of response letter

%\noindent
%Jan S. Hesthaven \\
%EPFL SB-DO\\
%PH A2 364 (B\^atiment PH)\\
%Station 3\\
%CH-1015 Lausanne \\
%Switzerland
%{
%\flushright{\today}\\
%}
% \vspace{0.3cm}
\noindent Dear Professor Hans De Sterck:\\[2ex]

We wish to submit the manuscript {\em Point spread function approximation of high rank Hessians with locally supported non-negative integral kernels} by Nick Alger, Tucker Hartland, Noemi Petra, and Omar Ghattas to be considered for publication in SISC in the {\em
  Numerical Algorithms for Scientific Computing} section.
%

In this manuscript, we propose an efficient point spread function (PSF) method for approximating matrix-free operators with locally supported non-negative integral kernels. We improve upon existing PSF methods by using a novel moment method for forming a-priori ellipsoid estimates for the supports of impulse responses. By solving an ellipsoid packing problem, we compute a large number of impulse responses per operator application, making the method highly efficient in terms of operator applications. We also provide an improved method for interpolating impulse responses based on a notion we call ``local mean displacement invariance,'' which generalizes classical local translation invariance. We apply the method to approximate high rank Hessians PDE constrained inverse problems. Our numerical results demonstrate that the proposed method outperforms conventional approaches, and that the method can approximate high rank Hessians with a small number of operator applies. The manuscript has not been submitted elsewhere for
publication.\\[1ex]

\noindent Thank you for your consideration.\\[3ex]

>>>>

\bigskip

\noindent Dear Professor Antil:\\[2ex]

Please find enclosed the revised manuscript ``Point spread function
approximation of high rank Hessians with locally supported
non-negative integral kernels'' by Nick Alger, Tucker Hartland, Noemi
Petra, and Omar Ghattas which we would like to resubmit to SISC in the
Numerical Algorithms for Scientific Computing section.

%
This cover letter is accompanied by a point-by-point list of responses
to the referees' comments. In addition, we have prepared a diff
document that highlights the differences between the initially
submitted and the new manuscript, where revisions are indicated by
color (blue represents new text, and red is deleted text). Please send
the diff document to the reviewers as well.

We would like to thank the reviewers for their careful reading of our article 
and their constructive feedback, and many thanks to you for handling the
manuscript.\\[3ex]
